Software architectures to integrate workflow engines in science gateways

### 2016-10-13 paper.tex
Fixed colors in tables

                                     & \cellcolor[HTML]{99A899}\correction{3}

@@

                                     & \cellcolor[HTML]{99D299}\textbf{\correction{9}}

@@

                                     & \cellcolor[HTML]{99FF99}\correction{1}

@@

                                     & \cellcolor[HTML]{99FF99}\textbf{\correction{2}}

@@

 Overall, task encapsulation performs a bit
better than the other architectures and nested workflows stand a bit
behind for the reasons mentioned previously.
\begin{table*}
\footnotesize
\centering
\begin{tabular}{rcccccc}
                                    & \textbf{Tight}
                                    & \textbf{Service}
                                    & \textbf{Task}
                                    & \textbf{Pool}
                                    & \textbf{Nested}
                                    & \textbf{Conversion} \\
                                    &&&&& \textbf{\correction{Service+Service}}&\\
  Integration (global score)    &
                                    \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99E899}{0.22}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99D299}{0.44}
                                    & \cellcolor[HTML]{999999}{1.00}
                                      & \cellcolor[HTML]{99DD99}{0.33}\\
Robustness (global score) &
                                \cellcolor[HTML]{99F099}{0.14}
                                    & \cellcolor[HTML]{99D399}{0.43}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99B699}{0.71}
                                    & \cellcolor[HTML]{999999}{1.00}
                                    & \cellcolor[HTML]{99D399}{0.43}\\
  Extensibility (global score)  & \cellcolor[HTML]{99D299}{0.44}
                                     & \cellcolor[HTML]{99D299}{\correction{0.22}}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99E899}{0.22}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99E899}{0.22}\\
Scalability (global score)  & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}\\
\correction{Functionality} (global score) & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}\\
                                    & \cellcolor[HTML]{99DA99}\textbf{1.6}
                                    & \cellcolor[HTML]{99B899}\textbf{\correction{2.4}}
                                    & \cellcolor[HTML]{99FF99}\textbf{0.5}
                                    & \cellcolor[HTML]{99BF99}\textbf{2.4}
                                    & \cellcolor[HTML]{999999}\textbf{3.5}
                                    & \cellcolor[HTML]{99DE99}\textbf{1.5}\\
\end{tabular}
\caption{Overall evaluation. Brighter colors and lower scores indicate better performance. Scores
  are obtained by summing the normalized global scores ($m'$ values) of
  each criterion in Table~\ref{table:evaluation} and the colors are obtained as in Table~\ref{table:evaluation}. }
\label{table:overall}
\end{table*}

>>>>

                                     & \cellcolor[HTML]{99C599}\correction{3}

@@

                                     & \cellcolor[HTML]{99E899}\textbf{\correction{9}}

@@

                                     & \cellcolor[HTML]{999999}\correction{1}

@@

                                     & \cellcolor[HTML]{999999}\textbf{\correction{2}}

@@

 Overall, task encapsulation performs a bit
better than the other architectures and nested workflows stand a bit
behind for the reasons mentioned previously.
\begin{table*}
\footnotesize
\centering
\begin{tabular}{rcccccc}
                                    & \textbf{Tight}
                                    & \textbf{Service}
                                    & \textbf{Task}
                                    & \textbf{Pool}
                                    & \textbf{Nested}
                                    & \textbf{Conversion} \\
                                    &&&&& \textbf{\correction{Service+Service}}&\\
  Integration (global score)    &
                                    \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99E899}{0.22}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99D299}{0.44}
                                    & \cellcolor[HTML]{999999}{1.00}
                                      & \cellcolor[HTML]{99DD99}{0.33}\\
Robustness (global score) &
                                \cellcolor[HTML]{99F099}{0.14}
                                    & \cellcolor[HTML]{99D399}{0.43}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99B699}{0.71}
                                    & \cellcolor[HTML]{999999}{1.00}
                                    & \cellcolor[HTML]{99D399}{0.43}\\
  Extensibility (global score)  & \cellcolor[HTML]{99D299}{0.44}
                                     & \cellcolor[HTML]{99E899}{\correction{0.22}}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99E899}{0.22}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99E899}{0.22}\\
Scalability (global score)  & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}\\
\correction{Functionality} (global score) & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{999999}{\correction{1.00}}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}\\
                                    & \cellcolor[HTML]{99FA99}\textbf{1.6}
                                    & \cellcolor[HTML]{99D299}\textbf{\correction{2.4}}
                                    & \cellcolor[HTML]{99FE99}\textbf{\correction{1.5}}
                                    & \cellcolor[HTML]{99D299}\textbf{2.4}
                                    & \cellcolor[HTML]{999999}\textbf{3.5}
                                    & \cellcolor[HTML]{99FF99}\textbf{1.5}\\
\end{tabular}
\caption{Overall evaluation. Brighter colors and lower scores indicate better performance. Scores
  are obtained by summing the normalized global scores ($m'$ values) of
  each criterion in Table~\ref{table:evaluation} and the colors are obtained as in Table~\ref{table:evaluation}. }
\label{table:overall}
\end{table*}
